Trends from 30-Year Observations of Downward Solar Irradiance in Thessaloniki, Greece

### 2024-11-02 appendix.tex
Commit 2024-11-02 22:14

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering
            \includegraphics[width=1.0\linewidth]{./images/SzaTrendsSeasTogether-2}
        }
    \end{adjustwidth}
    \caption{Long-term trends of SDR as a function of SZA separately form morning
           and afternoon periods, by season (rows of plots) for the three sky
           conditions (columns of plots).
           Solid shapes represent statistical significant trends ($p<0.005$), (\textbf{a}--\textbf{c}) winter, (\textbf{d}--\textbf{f}) spring, (\textbf{g}--\textbf{i}) summer, (\textbf{j}--\textbf{l}) autumn, and also (\textbf{a}, \textbf{d}, \textbf{g}, \textbf{j}) all-skies, (\textbf{b}, \textbf{e}, \textbf{h}, \textbf{k}) clear-skies and (\textbf{c}, \textbf{f}, \textbf{i}, \textbf{l}) cloudy-skies.
           Cases where $p<0.005$ or with less than $85$ observations may be
           missing from view.}\label{fig:SZAtrendSeason}
\end{figure}

>>>>

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering
            \includegraphics[width=1.0\linewidth]{./images/SzaTrendsSeasTogether-2}
        }
    \end{adjustwidth}
    \caption{Long-term trends of SDR as a function of SZA separately for morning
           and afternoon periods, by season (rows of plots) for the three sky
           conditions (columns of plots).
           Solid shapes represent statistical significant trends ($p<0.005$), (\textbf{a}--\textbf{c}) winter, (\textbf{d}--\textbf{f}) spring, (\textbf{g}--\textbf{i}) summer, (\textbf{j}--\textbf{l}) autumn, and also (\textbf{a}, \textbf{d}, \textbf{g}, \textbf{j}) all-skies, (\textbf{b}, \textbf{e}, \textbf{h}, \textbf{k}) clear-skies and (\textbf{c}, \textbf{f}, \textbf{i}, \textbf{l}) cloudy-skies.
           Cases where $p<0.005$ or with less than $85$ observations may be
           missing from view.}\label{fig:SZAtrendSeason}
\end{figure}
